Analysis plan

### 2023-02-06 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Continued work on the analysis plan

-   Proportion of days working onsite

-   Proportion of days working remote

-   Proportion of days working remote by the day of the week

@@

-   Indicator for an exit form employment

@@

-   Proportion of staff days working onsite

-   Proportion of staff days working remote

-   Proportion of staff days working remote by the day of the week

@@

@@

@@

```{r}
tbl %>% 
  flextable() %>% 
  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
  # set_header_labels(Group = "Level of analysis") %>% 
  merge_h(part = "header") %>% 
  merge_v(j = 1) %>% 
  theme_vanilla() %>% 
  autofit()
```
<!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->

@@

<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->

<!-- https://www.guru99.com/r-k-means-clustering.html -->

>>>>

-   Proportion of days onsite

-   Proportion of days remote

-   Proportion of days remote by the day of the week

@@

-   Number of working days

-   Indicator for an exit from employment

@@

-   Proportion of staff working days onsite

-   Proportion of staff working days remote

-   Proportion of staff working days remote by the day of the week

@@

-   Number of staff working days

@@

We have no plans to exclude any date.

@@

<!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->

@@

This is a descriptive study attempting to characterize the work patterns
of GSA staff as individuals and as teams. Work patterns will be
categorized by a rules-based approach and a supervised machine learning
approach called k-means clustering.

For the rules based approach, the portion of working days remote will be
the key variable to determine what category a staff or team will be in.
Staff will be grouped as follows:

1.  **All remote** - Staff who work remotely above the 95th percentile
    <!-- could be 75th -->
2.  **Mostly remote** - Staff who work remotely between the median and
    the 95th percentile <!-- could be 75th -->
3.  **Mostly onsite** - Staff who work remotely between 5th percentile
    and the median <!-- could be 25th -->
4.  **All onsite** - Staff who work remotely below the 5th percentile
    <!-- could be 75th -->

Teams will be categorized similarly:

1.  **All remote** - Teams that work remotely above the 95th percentile
    <!-- could be 75th -->
2.  **Mostly remote** - Teams that work remotely between the median and
    the 95th percentile <!-- could be 75th -->
3.  **Mostly onsite** - Teams that work remotely between 5th percentile
    and the median <!-- could be 25th -->
4.  **All onsite** - Teams that work remotely below the 5th percentile
    <!-- could be 75th -->

For the second categorization, a k-means clustering algorithm will be
used. We follow the methods layed out in:

-   [Cluster Analysis in
    R](https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/)

-   [K-means Clustering in R with
    Example](https://www.guru99.com/r-k-means-clustering.html)

-   [K-means clustering with tidy data
    principles](https://www.tidymodels.org/learn/statistics/k-means/)

For staff clusters, the following variables will be used to define the
clusters:

-   Proportion of days onsite

-   Proportion of days remote

-   Proportion of days remote by the day of the week

-   Number of working days

-   Average size of team over observation window

For team clusters, the following variables will be used:

-   Averages size of team over observation window

-   Proportion of staff working days onsite

-   Proportion of staff working days remote

-   Proportion of staff working days remote by the day of the week

-   Number of staff working days

All of the these variables will be scaled to reduce the effects of
outliers should they be present.

To determine the number appropriate number of clusters, several methods
exist. A rule of thumb to identify the correct number us to use

$$
\frac{\sqrt{NumberOfObservations}}{2}
$$
